\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemSimple}[1]{
  \item\small{
    {#1}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://alfredohdz.io}{\Large Jesús Alfredo Hernández Alarcón}} & \textbf{Email:} \href{mailto:alfredo.h.alarcon@icloud.com}{alfredo.h.alarcon@icloud.com}\\
  
  \href{https://alfredohdz.io}{https://alfredohdz.io} & \textbf{Mobile:} +52 55 7080 7972 \\
  & \textbf{Location:} Mexico \\
\end{tabular*}


%----------- Career Summary -----------------
\section{Career Summary}
Senior iOS Software Engineer with 10+ years of experience building scalable mobile applications for the fintech and banking sectors. Specialized in Swift, TDD, and modern iOS architectures (MVVM, VIPER, Clean Architecture). Proven track record of leading critical migrations from legacy codebases to modern, tested architectures, improving app performance by up to 80\%. Expert in developing secure authentication systems, biometric integrations, and complex user flows serving millions of users across LATAM. Strong advocate for clean code, SOLID principles, and agile methodologies.

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Stratominds}{México}
      {SCRUM Master Certification}{2018}
    \resumeSubheading
      {Apple Campus, UNAM}{México}
      {iOS Mobile Applications Development}{2018}
    \resumeSubheading
      {Universidad Nacional Autónoma de México}{México}
      {Bachelor in Computer Engineering}{2012 -- 2016}
  \resumeSubHeadingListEnd


%-----------Employment history and experience-----------------
\section{Employment history and experience}
  \resumeSubHeadingListStart
  
  \resumeSubheading
      {Ualá}{Mexico City, MX}
      {Senior iOS Software Engineer}{Nov 2021 - Oct 2025}
      \resumeItemListStart
        \resumeItem{Complete Onboarding Redesign (ARG \& MEX)}
          {Led the complete redesign and reengineering of the onboarding flow for Argentina and Mexico markets, migrating from a legacy monolithic architecture to a modern, modular design with comprehensive test coverage. Implemented new UI/UX aligned with design system standards and applied Clean Architecture principles with MVVM pattern.}
        \resumeItem{Document Capture Refactor}
          {Spearheaded a complete refactor of the ID and selfie capture feature, replacing a legacy implementation with a robust, test-driven solution. Achieved an 80\% improvement in capture success rate, reducing user friction and support tickets significantly.}
        \resumeItemSimple{Integrated biometric authentication (Face ID, Touch ID) using native Apple SDK and third-party solutions for the onboarding flow across 3 countries (Argentina, Mexico, Colombia).}
        \resumeItem{Screen Provider Framework}
          {Designed and developed a dynamic screen delivery system using JSON-driven configurations, enabling product teams to create and modify user flows without app releases. Collaborated closely with design, product, and engineering teams to establish reusable standards across the application.}
        \resumeItemSimple{Led migration from UIKit to SwiftUI for key features, implementing modern iOS APIs including async/await, Combine, and latest Swift language features.}
        \resumeItemSimple{Optimized app performance through improvements in local storage, caching strategies, feature flag management, and analytics implementation.}
        \resumeItemSimple{Applied TDD methodology throughout all feature development, significantly improving code quality and reducing regression bugs.}
      \resumeItemListEnd

    \resumeSubheading
      {Globant}{Mexico City, MX}
      {iOS Software Engineer}{July 2019 - Nov 2021}
      \resumeItemListStart
        \resumeItem{HSBC Mobile X}
          {Contributed to a global banking application serving millions of users across multiple markets. Implemented payment features, resolved critical bugs, and enhanced existing functionality for both local (Mexico) and international markets.}
        \resumeItemSimple{Collaborated effectively with cross-functional teams including developers, designers, QA engineers, project managers, and product owners in an agile environment.}
        \resumeItemSimple{Designed, developed, tested, released, and supported native iOS applications using the latest iOS and Xcode versions, following best practices and Apple Human Interface Guidelines.}
        \resumeItem{Instalment Payments Feature}
          {Developed and customized an instalment payment system specifically for the Mexican market, enabling users to split purchases into manageable payments.}
        \resumeItem{Digital Cards with Dynamic CVV}
          {Implemented a secure digital card feature with dynamic CVV generation for credit cards, deployed globally across all HSBC entities worldwide.}
        \resumeItem{CoDi QR Payment Integration}
          {Developed CoDi (Cobro Digital) integration allowing users to make payments via QR codes, a Mexico-specific feature enhancing local payment methods.}
      \resumeItemListEnd
      
      \resumeSubheading
      {IDEMIA}{Mexico City, MX}
      {Software Developer / Pre Sales Engineer}{Jan 2017 - July 2019}
      \resumeItemListStart
        \resumeItemSimple
        {Served as technical leader for LATAM development team, building biometric solutions and SDKs for the region.}
        \resumeItemSimple
        {Acted as technical consultant for clients, demonstrating biometric technology capabilities, implementation strategies, and best practices for secure biometric integration.}
        \resumeItemSimple
        {Developed proof-of-concepts and demo applications for pre-sales activities, showcasing IDEMIA's technologies on Android, iOS, and web platforms to prospective customers.}
        \resumeItem{Mobile Biometrics BioSmart SDK}
          {Developed mobile and web applications integrating facial recognition, fingerprint, and iris biometric technologies. Implemented integrations with various biometric hardware including readers, stations, and ATMs.}
        \resumeItemSimple
        {Documented software defects, performed SDK testing, and provided on-site client training for IDEMIA's biometric solutions.}
      \resumeItemListEnd
      
      \resumeSubheading
      {Tienda UNAM}{Mexico City, MX}
      {Android Developer}{Aug 2015 - Feb 2016}
      \resumeItemListStart
        \resumeItem{Main Android Application}
          {Developed the native Android application for Tienda UNAM, integrating Google Maps and other Google services.}
          \resumeItemSimple{Improved app architecture by migrating from MVC to MVP pattern, enhancing modularity and addressing performance issues.}
      \resumeItemListEnd
      
      \resumeSubheading
      {Nokia (Microsoft Mobile)}{Mexico City, MX}
      {Android Developer Intern}{Jan 2014 - July 2014}
      \resumeItemListStart
        \resumeItem{Nokia X Applications}
          {Developed Android applications compatible with Nokia X platform using Android Studio.}
          \resumeItemSimple{Successfully published multiple applications to the Nokia Store.}
      \resumeItemListEnd
      
  \resumeSubHeadingListEnd

\newpage
%----------- Languages -----------------
\section{Languages}
\begin{multicols}{2}
\begin{itemize}
	\item Spanish (Native)
	\item English (Professional Working Proficiency)
\end{itemize}
\end{multicols}

%--------Technical Skills------------
\section{Technical Skills}
\begin{itemize}
	\item \textbf{Languages \& Frameworks:} Swift, SwiftUI, UIKit, Combine, Objective-C
	\item \textbf{Architecture Patterns:} MVVM, MVP, VIPER, Clean Architecture, MVC
	\item \textbf{Development Practices:} TDD, Unit Testing, Integration Testing, UI Testing, SOLID principles
	\item \textbf{Tools \& Technologies:} Xcode, Git, CI/CD (Fastlane, Jenkins, GitHub Actions, Xcode Cloud), CocoaPods, SPM
	\item \textbf{Additional Skills:} REST APIs, JSON parsing, Core Data, UserDefaults, Keychain, Biometric authentication
	\item \textbf{Soft Skills:} Agile methodologies (SCRUM), cross-functional collaboration, technical leadership, code review
\end{itemize}


%-------------------------------------------
\end{document}